\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.2in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}


\name{Hrishikesh Barman} % Your name
\address{ \href{mailto:gigs@geekodour.com}{gigs@geekodour.org} \\ \href{https://github.com/geekodour}{github} \\ \href{https://geekodour.org/docs/documents/hire}{geekodour.org} }
\address{Remote \\ Guwahati, IN \\ Relocatable}

\begin{document}
% ----------------------------------------------------------------------------------------
%	OBJECTIVE
% ----------------------------------------------------------------------------------------

\begin{rSection}{SUMMARY}
  {Fullstack SWE with 2+ years of experience in data engineering and backend development with a strong interest in selfhosting, distributed systems, observability and automation seeking full-time system infrastructure role.}
\end{rSection}

% ----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS
% ----------------------------------------------------------------------------------------
\begin{rSection}{Relevant skills}
  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Operating infra & AWS, GCP, Ansible, Nix, Kubernetes, Nagios, Prometheus\\
    Managing systems & Containers\&VMs, linux systems skills\\
    Handing distributed systems & RPC, decentralized databases, message brokers, P2P\\
    Network\&Security & SSH, Tailscale, Troubleshooting\\
    % \\
    Tools\&Automation & Golang, Python, C++, JavaScript, Lua, Bash, CI/CD systems and CLI tools.\\
    Managing code and docs & Git, org-mode, markdown\\
    % \\
    Data engineering & Kafka, Airflow, BigQuery, PyData stack, Datasette, Metabase, other similar tools\\
    % \\
    Building backends & Golang, NodeJS, Python, OCalm, Ruby\\
    Working with databases & PostgreSQL, MongoDB, SQLite\\
    Basic web applications & TypeScript, React, HTML5, CSS\\
    Complex web applications & WebRTC, Websockets, WebAssembly, Browser performance\\
  \end{tabular}\
\end{rSection}

\begin{rSection}{relevant EXPERIENCE}
  \textbf{Data Engineer} \hfill August 2020 — March 2022\\
  Clarisights \hfill \textit{Bangalore, IN}
  \begin{itemize}
    \itemsep -3pt {}
    \item Designed and implemented several integrations to the ETL pipeline, ensuring efficiency in I/O. Mostly involved Ruby, MongoDB and PostgreSQL along with some Python with a pinch of Airflow.
    \item Was part of weekly on-calls addressing both system and customer issues. Built integrations in the stringent deadlines which helped in securing key business partnerships for the company.
  \end{itemize}

  \textbf{Google Summer of Code Student} \hfill May 2019 — August 2019\\
  CNCF/Prometheus (\href{https://blog.geekodour.org/posts/gsoc19/}{follow-up}) \hfill \textit{Remote}
  \begin{itemize}
    \itemsep -3pt {}
    \item Worked on refining the release benchmarking system for Prometheus called Prombench. This involved working with Grafana, Containers, Kubernetes(GKE), CI/CD systems and lots of Go.
    \item The outcome of this effort was a heightened level of scrutiny into the Prombench system, providing developers with increased flexibility to compare different Prometheus versions with greater precision.
  \end{itemize}

  \textbf{SysAdmin Intern} \hfill August 2018 — December 2018\\
  Free Software Foundation \href{https://www.fsf.org/blogs/sysadmin/what-i-learned-during-my-internship-with-the-fsf-tech-team}{(follow-up)} \hfill \textit{Remote}
  \begin{itemize}
    \itemsep -3pt {}
    \item Evaluated the feasibility of replacing the Nagios with Prometheus. My primary responsibilities included the development of Ansible roles and create various scripts to support the implementation using python, shell scripts and go.
  \end{itemize}

  \textbf{Freelance Developer} \hfill November 2015 — Present\\
  Individual Contributor \hfill \textit{Remote}
  \begin{itemize}
    \itemsep -3pt {}
    \item Delivering functional, documented and tested code for clients globally.
    \item Previously worked with bespoke web applications, extensions/plugins, automation scripts/bots/scrapers.
  \end{itemize}

\end{rSection}

% ----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
% ----------------------------------------------------------------------------------------

\begin{rSection}{relevant PROJECTS}
  \vspace{-1.25em}
  \item \textbf{wscribe-editor} {A transcript editor for whisper generations \href{https://github.com/geekodour/wscribe-editor}{(source)}} \hfill 2023
  \item \textbf{threesixfive daily} {A digest that refreshes daily from a curated database \href{https://daily.threesixfive.shop/}{(check it out)}
  } \hfill 2022
  \item \textbf{gitpushblog} {A git based blog engine \href{https://github.com/geekodour/gitpushblog}{(source)}} \hfill 2017
  \item \textbf{projects \& experiments} {Complete list of \href{https://geekodour.org/docs/updates/projects/}{projects} and
 \href{https://geekodour.org/docs/updates/experiments/}{experiments}
  } \hfill 2013 - Present
\end{rSection}

% ----------------------------------------------------------------------------------------
% ----------------------------------------------------------------------------------------
\begin{rSection}{Other Activities}
  \vspace{-1.25em}
    \item Opensource: Actively contributed, organized and mentored in the OSS community \hfill 2016-2020
    \item Hackathons: Won few, but doesn't matter. Had fun. \hfill 2014-2019
\end{rSection}

% ----------------------------------------------------------------------------------------
%	EDUCATION SECTION
% ----------------------------------------------------------------------------------------

% \begin{rSection}{Education}

%   {\bf B.Tech Computer Science}, GIMT Guwahati \hfill {2015 — 2018(Dropped)}

% \end{rSection}


\end{document}
